Pyro-Velocity: Probabilistic RNA Velocity inference from single-cell data

### 2024-08-20 reproducibility/manuscript/manuscript.qmd
docs(manuscript): enable pandoc reference-doc
Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

---
title: "Pyro-Velocity: Probabilistic RNA Velocity inference from single-cell data"
format:
  nature-pdf:
    # journal.cite-style is included in the tex file but ignored by pandoc if 
    # cite-method is not `natbib`.
    journal:
      cite-style: sn-nature
    classoption: 
      - lineno
    # `citeproc` is the pandoc default. Set `cite-method: natbib` if required
    # to use the bst styles from the upstream template.
    cite-method: citeproc
    keep-tex: true
    equal-margins: false
    include-in-header: header.tex
  html:
    code-fold: true
    html-math-method: mathjax
  docx: default
csl: _extensions/sciexp/nature/csl/springer-basic-brackets-no-et-al.csl
author:
  - name: Qian Qin
    affiliations:
      - name: Massachusetts General Hospital Research Institute, Charlestown, MA
        id: 1
        department: Molecular Pathology Unit
        city: Charlestown
        state: MA
        postal-code: 02129
      - name: Harvard Medical School, Charlestown, MA
        id: 2
        department: Massachusetts General Hospital Cancer Center
        city: Charlestown
        state: MA
        postal-code: 02129
      - name: Massachusetts General Hospital, Boston, MA
        id: 3
        department: Center for Regenerative Medicine
        city: Boston
        state: MA
        postal-code: 02114
      - name: Harvard University, Cambridge, MA
        id: 4
        department: Harvard Stem Cell Institute
        city: Cambridge
        state: MA
        postal-code: 02139
      - name: Cambridge, MA
        id: 5
        department: Broad Institute of MIT and Harvard
        city: Cambridge
        state: MA
        postal-code: 02142
    # attributes:
    #   equal-contributor: true
  - name: Eli Bingham
    affiliations:
      - ref: 5
      - name: Cambridge, MA
        id: 7
        department: Basis Research Institute
        city: Cambridge
        state: MA
        postal-code: 02142
  - name: Gioele La Manno
    affiliations:
      - name: Laboratory of Neurodevelopmental Systems Biology, Lausanne, Switzerland
        id: 6
        department: Brain and Mind Institute, School of Life Sciences, École Polytechnique Fédérale de Lausanne (EPFL)
        city: Lausanne
        state: Switzerland
        postal-code: 1015
    email: gioele.lamanno@epfl.ch
    attributes:
      corresponding: true
  - name: David M. Langenau
    affiliations:
      - ref: 1
      - ref: 2
      - ref: 3
      - ref: 4
    email: dlangenau@mgh.harvard.edu
    attributes:
      corresponding: true
  - name: Luca Pinello
    affiliations:
      - ref: 1
      - ref: 2
      - ref: 5
    email: lpinello@mgh.harvard.edu
    attributes:
      corresponding: true
abstract: |
  Single-cell RNA Velocity has dramatically advanced our ability to model cellular differentiation and cell fate decisions. However, current preprocessing choices and model assumptions often lead to errors in assigning developmental trajectories. Here, we develop, Pyro-Velocity, a Bayesian, generative, and multivariate RNA Velocity model to estimate the uncertainty of cell future states. This approach models raw sequencing counts with the synchronized cell time across all expressed genes to provide quantifiable and improved information on cell fate choices and developmental trajectory dynamics.
keywords: [RNA velocity, single-cell RNA sequencing, probabilistic generative modeling, cell fate, developmental trajectory inference]
bibliography: bibliography.bib
crossref:
  custom:
    - kind: float
      key: suppfig
      latex-env: suppfig
      reference-prefix: Figure S
      space-before-numbering: false
      latex-list-of-description: Supplementary Figure
---

>>>>

---
title: "Pyro-Velocity: Probabilistic RNA Velocity inference from single-cell data"
format:
  nature-pdf:
    # journal.cite-style is included in the tex file but ignored by pandoc if 
    # cite-method is not `natbib`.
    journal:
      cite-style: sn-nature
    classoption: 
      - lineno
    # `citeproc` is the pandoc default. Set `cite-method: natbib` if required
    # to use the bst styles from the upstream template.
    cite-method: citeproc
    keep-tex: true
    equal-margins: false
    include-in-header: header.tex
  html:
    code-fold: true
    html-math-method: mathjax
  docx:
    reference-doc: styles.docx
csl: _extensions/sciexp/nature/csl/springer-basic-brackets-no-et-al.csl
author:
  - name: Qian Qin
    affiliations:
      - name: Massachusetts General Hospital Research Institute, Charlestown, MA
        id: 1
        department: Molecular Pathology Unit
        city: Charlestown
        state: MA
        postal-code: 02129
      - name: Harvard Medical School, Charlestown, MA
        id: 2
        department: Massachusetts General Hospital Cancer Center
        city: Charlestown
        state: MA
        postal-code: 02129
      - name: Massachusetts General Hospital, Boston, MA
        id: 3
        department: Center for Regenerative Medicine
        city: Boston
        state: MA
        postal-code: 02114
      - name: Harvard University, Cambridge, MA
        id: 4
        department: Harvard Stem Cell Institute
        city: Cambridge
        state: MA
        postal-code: 02139
      - name: Cambridge, MA
        id: 5
        department: Broad Institute of MIT and Harvard
        city: Cambridge
        state: MA
        postal-code: 02142
    # attributes:
    #   equal-contributor: true
  - name: Eli Bingham
    affiliations:
      - ref: 5
      - name: Cambridge, MA
        id: 7
        department: Basis Research Institute
        city: Cambridge
        state: MA
        postal-code: 02142
  - name: Gioele La Manno
    affiliations:
      - name: Laboratory of Neurodevelopmental Systems Biology, Lausanne, Switzerland
        id: 6
        department: Brain and Mind Institute, School of Life Sciences, École Polytechnique Fédérale de Lausanne (EPFL)
        city: Lausanne
        state: Switzerland
        postal-code: 1015
    email: gioele.lamanno@epfl.ch
    attributes:
      corresponding: true
  - name: David M. Langenau
    affiliations:
      - ref: 1
      - ref: 2
      - ref: 3
      - ref: 4
    email: dlangenau@mgh.harvard.edu
    attributes:
      corresponding: true
  - name: Luca Pinello
    affiliations:
      - ref: 1
      - ref: 2
      - ref: 5
    email: lpinello@mgh.harvard.edu
    attributes:
      corresponding: true
abstract: |
  Single-cell RNA Velocity has dramatically advanced our ability to model cellular differentiation and cell fate decisions. However, current preprocessing choices and model assumptions often lead to errors in assigning developmental trajectories. Here, we develop, Pyro-Velocity, a Bayesian, generative, and multivariate RNA Velocity model to estimate the uncertainty of cell future states. This approach models raw sequencing counts with the synchronized cell time across all expressed genes to provide quantifiable and improved information on cell fate choices and developmental trajectory dynamics.
keywords: [RNA velocity, single-cell RNA sequencing, probabilistic generative modeling, cell fate, developmental trajectory inference]
bibliography: bibliography.bib
crossref:
  custom:
    - kind: float
      key: suppfig
      latex-env: suppfig
      reference-prefix: Figure S
      space-before-numbering: false
      latex-list-of-description: Supplementary Figure
---
